Automatic Identification and Annotation of Tasks in Structured Programs

### 2018-01-20 docs/ACM/paper.tex
Working on Section 3.

\begin{definition}[Task]
\label{def:task}
Given a program $P$, a task $T$ is a tuple $(G', M)$ formed by a hammock region
$G'$, plus a set $M$ of memory regions that represent the dependences of $T$.
\end{definition}

Definition~\ref{def:task} uses the concept of {\em memory region}.
Syntactically, memory regions are described by program variables and/or pointers
plus ranges of offsets that these pointers are allowed to dereference.
If a task $(T_1, M_1)$ writes onto a memory region $m$, and task
$(T_2, M_2)$ contains code that reads $m$, then $m \in M_1$, to ensure that
dependences are respected.
If a program $P$ is partitioned into a set of $n$ tasks $\{(T_1, M_1),
\ldots (T_n, M_n)\}$, then this partition is said to be {\em correct} if any
topological ordering of the tasks, as determined by dependence relations, always
leads to the same results as the sequential execution of $P$.

>>>>

\begin{definition}[Task]
\label{def:task}
Given a program $P$, a task $T$ is a tuple $(G', M_i, M_o)$ formed by a hammock
region $G'$, plus a set $M_i$ of memory regions representing data that $T$ reads,
and a set $M_o$ of memory regions representing data that $T$ writes.
\end{definition}

Definition~\ref{def:task} uses the concept of {\em memory region}.
Syntactically, memory regions are described by program variables and/or pointers
plus ranges of offsets that these pointers are allowed to dereference.
Given two tasks: $T_1 = (G_1, M_{i1}, M_{o1})$ and $T_2 = (G_2, M_{i2}, M_{o2})$,
if $M_{o1} \cap M_{i2} \neq \emptyset$, then we say that $T_2$ {\em depends} on
$T_1$.
If a program $P$ is partitioned into a set of $n$ tasks, then this partition is
said to be {\em correct} if: (i) it does not contain cyclic dependence relations;
and (ii) any topological ordering of the tasks, as determined by dependence
relations, leads to the same results as the sequential execution of $P$.
